{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-01-14 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

        Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used Theorem \ref{thm:prox-grad-ineq} which yields the inequality that we want to prove. 

@@

            \todo{
                $\blacksquare$ Add these. $\blacksquare$ Cite these. 
            }{(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
            \todoinline{\noindent
                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
                For more information, see:  
                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 

@@

            This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by \hl{Tibshirani} \cite{tibshirani_regression_1996}. 

@@

        \subsubsection{Discussion}
            We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
            Our goal here is to show that this silly idea is absolutely ungrounded. 
            However, two things are clear. FR-WAPG performs better than V-FISTA and it doesn't require prior knowledge on parameter $L, \mu$. 
            \par
            The results of R-WAPG is relevent because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence. 
            Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
            Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
            \begin{align*}
                \alpha_{k + 1} 
                &= 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
                \right)
                \\
                &= 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{
                        (\alpha_k^2 - q + 2)^2 + 2q - 4
                    }
                \right)
                \\
                &< 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{
                        (\alpha_k^2 - q + 2)^2
                    }
                \right) \le 1. 
            \end{align*}
            Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
            Therefore, $\alpha_k \in (0, 1)$. 
            In the very unlikely case when $q = 1$

>>>>

        Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used Theorem \ref{thm:prox-grad-ineq} which yields the desired inequality. 

@@

            (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}. 
            % \todoinline{\noindent
            %     The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
            %     For more information, see:  
            %     \begin{enumerate}
            %         \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
            %         \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
            %     \end{enumerate}
            % }

@@

            This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by Tibshirani \cite{tibshirani_regression_1996}. 

@@

        \subsubsection{Discussion}
            We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
            Our numericaly experiments are explorative. 
            Nontheless, two things are clear. FR-WAPG performs better than V-FISTA on the first hundreds of iterations and it doesn't require prior knowledge on parameter $L, \mu$. 
            \par
            From a theoretical perspective, the results of R-WAPG is relevent to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence. 
            Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
            Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
            \begin{align*}
                \alpha_{k + 1} 
                &= 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
                \right)
                \\
                &= 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{
                        (\alpha_k^2 - q + 2)^2 + 2q - 4
                    }
                \right)
                \\
                &< 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{
                        (\alpha_k^2 - q + 2)^2
                    }
                \right) \le 1. 
            \end{align*}
            Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
            Therefore, $\alpha_k \in (0, 1)$. 
            In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
            The difficulty here is that it's impossible to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
            It would require more knowledge about the trajectory taken for a specific initial guess. 
            \par 
            From a practical point of view, the numerical experiments shows that at the start, the estimate for $\mu$ can be very lose.
            This is partially explained by the remark of of Proposition \ref{prop:stepwise-lyapunov}. 
            It also showed that the function value gives very similar charactercteristics of M-FISTA. 
            This hinted at the fact that the sequence $(\alpha_k)_{k \ge 0}$ may has something to do with restarting.
            \par
            Finally, we note that in practice, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.
